\textit{Supplementary materials for:} Fitness tracking reveals task-specific associations between memory, mental health, and exercise

### 2021-10-22 paper/supplement.tex
addressed all coauthor comments, additional round of JRM edits, updated figs

\begin{figure}[p]
\centering
\includegraphics[width=0.6\textwidth]{figs/devices}
\caption{\textbf{Fitbit devices.}  The bars indicate the numbers of
  participants whose fitness tracking data came from each model of
  Fitbit device.  ``MobileTrack'' refers to participants who used
  smartphone accelerometer information to track their activity via the
  Fitbit smartphone app.
  ``Unknown''  denotes participants whose device information was not
  available from their available Fitbit data.}
\label{fig:devices}
\end{figure}

@@

Out-of-range HR         & Number of daily minutes spent with a heart rate lower than the "fat burn" heart rate zone (50\% of the maximum heart rate); maximum heart rate is defined as 220 minus age, in years & minutes (min)                            \\

@@

\begin{sidewaysfigure}[p]
  \centering
  \includegraphics[width=0.75\textwidth]{figs/weighted_timecourse_activity_MH}
\caption{\textbf{History of fitness activity levels weighted by
    mental health factors.}  This figure is in the same format as
  Figure~\dynamics c, but shows additional fitness-related measures (Tab.~\ref{tab:abbreviations}).}
\label{fig:activity_timecourse_MH}
\end{sidewaysfigure}

\begin{sidewaysfigure}[p]
  \centering
  \includegraphics[width=\textwidth]{figs/weighted_timecourse_HR_MH}
\caption{\textbf{History of cardiovascular activity weighted by
    mental health factors.} This figure is in the same format as
  Figure~\dynamics c, but shows additional fitness-related measures (Tab.~\ref{tab:abbreviations}).}
\label{fig:HR_timecourse_MH}
  \end{sidewaysfigure}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.75\textwidth]{figs/weighted_timecourse_sleep_MH}
\caption{\textbf{History of sleep efficiency and duration weighted by
    mental health factors.} This figure is in the same format as
  Figure~\dynamics c, but shows additional fitness-related measures (Tab.~\ref{tab:abbreviations}).}
\label{fig:sleep_timecourse_MH}
  \end{figure}

>>>>

\begin{figure}[p]
\centering
\includegraphics[width=0.6\textwidth]{figs/devices}
\caption{\textbf{Fitbit devices.}  The bars indicate the numbers of
  participants whose fitness tracking data came from each model of
  Fitbit device.  ``MobileTrack'' refers to participants who used
  smartphone accelerometer information to track their activity via the
  Fitbit smartphone app.
  ``Unknown''  denotes participants whose device information was not
  specified in their Fitbit data.}
\label{fig:devices}
\end{figure}

@@

Out-of-range HR, OOR mins         & Number of daily minutes spent with a heart rate lower than the "fat burn" heart rate zone (50\% of the maximum heart rate); maximum heart rate is defined as 220 minus age, in years & minutes (min)                            \\

@@

\begin{sidewaysfigure}[p]
  \centering
  \includegraphics[width=0.75\textwidth]{figs/weighted_timecourse_activity_MH}
\caption{\textbf{History of fitness activity levels weighted by
    mental health factors.}  This figure is in the same format as
  Figure~\dynamics c, but shows additional fitness-related and mental
  health-related measures (Tab.~\ref{tab:abbreviations}).}
\label{fig:activity_timecourse_MH}
\end{sidewaysfigure}

\begin{sidewaysfigure}[p]
  \centering
  \includegraphics[width=\textwidth]{figs/weighted_timecourse_HR_MH}
\caption{\textbf{History of cardiovascular activity weighted by
    mental health factors.} This figure is in the same format as
  Figure~\dynamics c, but shows additional fitness-related and mental
  health-related measures (Tab.~\ref{tab:abbreviations}).}
\label{fig:HR_timecourse_MH}
  \end{sidewaysfigure}

\begin{figure}[p]
  \centering
  \includegraphics[width=0.75\textwidth]{figs/weighted_timecourse_sleep_MH}
\caption{\textbf{History of sleep efficiency and duration weighted by
    mental health factors.} This figure is in the same format as
  Figure~\dynamics c, but shows additional fitness-related and mental
  health-related measures (Tab.~\ref{tab:abbreviations}).}
\label{fig:sleep_timecourse_MH}
  \end{figure}
